---

---
**Load the packages**
```{r,echo=FALSE,results='hide',message=FALSE}
library(knitr)
library(ggplot2)
library(xtable)
library(arules)
library(arulesViz)
library(RColorBrewer)
```

**Read the Item Level Data File**
```{r,echo=FALSE,message=FALSE}
snack <- read.csv("C:/Users/Prasanta/Documents/snacks_item.csv", h=T)
#Dimension of the File
dim(snack)
```

**Names of Columns**
```{r, echo=FALSE,message=FALSE}
colnames(snack)
```


**Find the number of unique customers**
```{r, echo=FALSE,message=FALSE}
length(unique(snack$CUSTOMER_NO))
```

**Number of Unique SKU**
```{r,echo=FALSE,message=FALSE}
length(unique(snack$SKU))
```

**Total Transactions and SKUs in the Data**
```{r,echo=FALSE,message=FALSE}
groc <- read.transactions("C:/Users/Prasanta/Documents/sku_bas2.csv", format = "single",sep= ",", cols = c(1,2),rm.duplicates=TRUE)
groc
```

**Summary Statistics of Market Basket**
```{r,echo=FALSE,message=FALSE}
summary(groc)
```

**Histogram of Top 20 SKUs**
```{r,echo=FALSE,message=FALSE, fig.width = 6}
#inspect(groc[1:3])
itemFrequencyPlot(groc, topN = 20)
```

**Developing Association Rules using Apriori Algorithm for Support = .007 and Confidence = 25%**
```{r,echo=FALSE,message=FALSE}
m1 <- apriori(groc, parameter = list(support = .007, confidence = 0.25, minlen=2))
m1
inspect(m1)
```

**Create Visualization**
```{r,echo=FALSE,message=FALSE, fig.height=5}
plot(m1, measure=c("support" , "confidence") ,control=list(col=brewer.pal(11,"Spectral")),main="", shading="lift")
plot(m1, measure=c("support" , "lift") , control=list(col=brewer.pal(11,"Spectral")),main="",shading="confidence")
```

```{r,echo=FALSE,message=FALSE}
plot(m1, method="matrix" , measure="lift" ,control=list(col=brewer.pal(11,"Spectral")),main="")
plot(m1, method="matrix3D" ,measure=c("lift", "confidence"))
```

**Generating Association Rules for Support = .001  and Confidence = 35%**
```{r,echo=FALSE,message=FALSE,fig.height=12, fig.width=11}
#plot(m1, method="matrix" , measure="lift" , interactive=TRUE )
m2 <- apriori(groc, parameter = list(support = .001, confidence = 0.35, minlen=2))
m2
inspect(m2)
plot(m2, method="graph",control=list(type="items",main=""))
```

**Sorting the Top 10 Association Rules by Lift**
```{r,echo=FALSE,message=FALSE, fig.height=7, fig.width=8.5}
inspect(sort(m2, by = "lift")[1:10])
subrules2 <- head(sort(m2, by="lift"), 10)
plot(subrules2, method="graph",control=list(type="items",main=""))
```

**Sorting the Top 10 Association Rules by Confidence**
```{r,echo=FALSE,message=FALSE, fig.height=7, fig.width=8.5}
inspect(sort(m2, by = "confidence")[1:10])
ubrules2 <- head(sort(m2, by="lift"), 10)
plot(subrules2, method="graph",control=list(type="items",main=""))
```

**Create Visualization**
```{r,echo=FALSE,message=FALSE,fig.height=6, fig.width=8}
plot(m2, measure=c("support" , "confidence") , control=list(col=brewer.pal(11,"Spectral")),main="",shading="lift")
plot(m2, measure=c("support" , "lift") ,control=list(col=brewer.pal(11,"Spectral")),main="", shading="confidence")
````

```{r,echo=FALSE,message=FALSE,fig.height=6, fig.width=8}
plot(m2, method="matrix" , measure="lift",control=list(col=brewer.pal(11,"Spectral")),main="" )
plot(m2, method="matrix3D" ,measure=c("lift", "confidence"))
```
